### 2010-09-17 proposal/preProposal.tex
Changed workplan.

Once we begin working with the robot and have an idea of the algorithm
we will use, we will divide the work among us.

>>>>

The first week we will work together on making the robot move. Until we get the platrom ready to run our code, it will be difficult to separate the tasks. However, once we begin implementing our chosen algorithms, this division will become more clear.
